---
title: "UN Report Relationship GDP LifeExpectancy"
author: "Feriel P"
date: "2023-05-25"
output: html_document
---

```{r setup, include=FALSE}
#include=FALSE means this chunk of code and its output will not be included in the report
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE} 
library(tidyverse)
```
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country's economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.
```{r load_data, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```
```{r gdp_lifeExp_1997, echo=FALSE}
#echo=FALSE means that this chunk of code will not be shown in the report, but the output from this chunk will be in the report
library(ggplot2)
ggplot(data = gapminder_1997) +
  aes(x=gdpPercap, y=lifeExp, color = continent, size = pop/1000000) +
  geom_point() +
  labs(x= "GDP per capita", y="Life expectancy", title = "Do people in wealthy countries live longer?",
  size = "Population (in millions)", color = "Continents")
```
```{r, include=FALSE}
nCountries <- gapminder_1997 %>% select(country) %>%  n_distinct()
minGDP <- gapminder_1997 %>% summarize(round(min(gdpPercap))) %>% pull()
maxGDP <- gapminder_1997 %>% summarize(round(max(gdpPercap))) %>% pull()
#If pull() wasn't used we would get a tibble assigned to the variable, not the value
```

The plot above shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` distinct countries. For this set of countries, economic wealth ranged from a minimum of USD `r minGDP` to a maximum of USD `r maxGDP` per capita.

| HEADER 1 | HEADER 2 |
|----------|----------|
|row 1, column 1 |row 1, column 2 |
|row 2, column 1 |row 2, column 2 |


```{r kable_table, echo=FALSE}
library(knitr)
gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable()

```


